\chapter{References}
\addcontentsline{toc}{chapter}{References}

\begin{thebibliography}{99}

\bibitem{ref1}
A. Reda and A. Andreas,
``Solar Position Algorithm for Solar Radiation Applications,''
\textit{Solar Energy}, vol. 76, no. 5, pp. 577--589, 2004.

\bibitem{ref2}
J. Deitsch, D. Christlein, C. Berger, A. Buerhop, F. Maier, J. Gallwitz and C. Riess,
``Automatic Classification of Defective Photovoltaic Module Cells in Electroluminescence Images,''
\textit{Solar Energy}, vol. 185, pp. 455--468, 2019.

\bibitem{ref3}
M. Dhimish and V. Holmes,
``Survey of Photovoltaic Cell Defects Using Electroluminescence and Infrared Imaging,''
\textit{Renewable and Sustainable Energy Reviews}, vol. 70, pp. 828--837, 2017.

\bibitem{ref4}
J. A. Tsanakas, L. Ha and C. Buerhop,
``Faults and Infrared Thermographic Diagnosis in Operating Solar Photovoltaic Plants,''
\textit{Renewable Energy}, vol. 133, pp. 139--148, 2019.

\bibitem{ref5}
A. Krizhevsky, I. Sutskever and G. Hinton,
``ImageNet Classification with Deep Convolutional Neural Networks,''
\textit{Advances in Neural Information Processing Systems}, vol. 25, 2012.

\bibitem{ref6}
K. He, X. Zhang, S. Ren and J. Sun,
``Deep Residual Learning for Image Recognition,''
\textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}, pp. 770--778, 2016.

\bibitem{ref7}
Y. LeCun, Y. Bengio and G. Hinton,
``Deep Learning,''
\textit{Nature}, vol. 521, no. 7553, pp. 436--444, 2015.

\bibitem{ref8}
I. Goodfellow, Y. Bengio and A. Courville,
\textit{Deep Learning},
MIT Press, 2016.

\bibitem{ref9}
R. C. Gonzalez and R. E. Woods,
\textit{Digital Image Processing},
4th ed., Pearson Education, 2018.

\bibitem{ref10}
R. Szeliski,
\textit{Computer Vision: Algorithms and Applications},
Springer, 2022.

\bibitem{ref11}
J. Redmon and A. Farhadi,
``YOLOv3: An Incremental Improvement,''
\textit{arXiv Preprint arXiv:1804.02767}, 2018.

\bibitem{ref12}
A. Bochkovskiy, C. Wang and H. Liao,
``YOLOv4: Optimal Speed and Accuracy of Object Detection,''
\textit{arXiv Preprint arXiv:2004.10934}, 2020.

\bibitem{ref13}
S. Ren, K. He, R. Girshick and J. Sun,
``Faster R-CNN: Towards Real-Time Object Detection with Region Proposal Networks,''
\textit{IEEE Transactions on Pattern Analysis and Machine Intelligence},
vol. 39, no. 6, pp. 1137--1149, 2017.

\bibitem{ref14}
P. Viola and M. Jones,
``Rapid Object Detection Using a Boosted Cascade of Simple Features,''
\textit{IEEE Conference on Computer Vision and Pattern Recognition}, 2001.

\bibitem{ref15}
T.-Y. Lin et al.,
``Microsoft COCO: Common Objects in Context,''
\textit{European Conference on Computer Vision (ECCV)},
pp. 740--755, 2014.

\bibitem{ref16}
M. Everingham, L. Van Gool, C. Williams, J. Winn and A. Zisserman,
``The Pascal Visual Object Classes Challenge,''
\textit{International Journal of Computer Vision},
vol. 88, no. 2, pp. 303--338, 2010.

\bibitem{ref17}
J. Deng et al.,
``ImageNet: A Large-Scale Hierarchical Image Database,''
\textit{IEEE Conference on Computer Vision and Pattern Recognition},
pp. 248--255, 2009.

\bibitem{ref18}
C. Szegedy et al.,
``Going Deeper with Convolutions,''
\textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)},
2015.

\bibitem{ref19}
D. P. Kingma and J. Ba,
``Adam: A Method for Stochastic Optimization,''
\textit{International Conference on Learning Representations (ICLR)},
2015.

\bibitem{ref20}
F. Chollet,
\textit{Deep Learning with Python},
2nd ed., Manning Publications, 2021.

\bibitem{ref21}
OpenCV Development Team,
``OpenCV Library Documentation,''
Available online: \texttt{https://opencv.org}

\bibitem{ref22}
J. Long, E. Shelhamer and T. Darrell,
``Fully Convolutional Networks for Semantic Segmentation,''
\textit{IEEE Conference on Computer Vision and Pattern Recognition (CVPR)},
pp. 3431--3440, 2015.

\bibitem{ref23}
A. Dosovitskiy et al.,
``An Image is Worth 16x16 Words: Transformers for Image Recognition at Scale,''
\textit{ICLR}, 2021.

\bibitem{ref24}
G. Jocher, A. Chaurasia and J. Qiu,
``Ultralytics YOLO Documentation,''
Ultralytics, 2024.

\bibitem{ref25}
A. Buerhop-Lutz et al.,
``Machine Learning for Automated Inspection of Photovoltaic Systems: A Review,''
\textit{Progress in Photovoltaics},
vol. 30, no. 5, pp. 567--587, 2022.

\bibitem{ref26}
Y. Gao, X. Li and Z. Wang,
``Deep Learning Based Defect Detection for Solar Panels Using UAV Images,''
\textit{IEEE Access},
vol. 9, pp. 124567--124578, 2021.

\bibitem{ref27}
M. Shams, A. Rahman and S. Hossain,
``Automatic Solar Panel Defect Detection Using YOLO-Based Object Detection Models,''
\textit{Applied Sciences},
vol. 13, no. 4, pp. 2145--2160, 2023.

\bibitem{ref28}
S. Kumar and P. Singh,
``Drone-Based Visual Inspection Framework for Large-Scale Solar Farms,''
\textit{Renewable Energy},
vol. 210, pp. 1190--1202, 2023.

\bibitem{ref29}
M. A. Islam, R. Rahman and T. Hasan,
``Artificial Intelligence Techniques for Solar Farm Monitoring and Maintenance: A Review,''
\textit{Sustainable Energy Technologies and Assessments},
vol. 57, 2023.

\bibitem{ref30}
Z. Chen, Y. Liu and H. Zhao,
``YOLO-Based Photovoltaic Fault Detection and Classification Using RGB Images,''
\textit{Scientific Reports},
vol. 14, 2024.

\end{thebibliography}
